---
title: "10-import"
output: html_notebook
---

# Loading the needed libraries

```{r install_packages, warning=FALSE, include=FALSE}
library(dplyr)
library(janitor)
library(readxl)
library(tidyverse)
library(ggplot2)
library(ggalluvial)
library(tidyr)
library(assertr)
library(lubridate)
```

# Loading the data

The dataset that I have selected for this project contains information on every known satellite orbitting the Earth. 

This is a database compiled by the Union of Concerned Scientists. It contains information on more than 2000 live satellites. The dataset is updated "roughly quarterly." The following information is available in the dataset:

* Name of Satellite
* Country of origin
* Country of operator
* Operating organization
* Users
* Purpose
* Orbit type
* Orbit class
* Information about orbit (eccentricity, inclination etc)
* Date of Launch + Other launch details (location, launch vehicle etc.)
* Expected lifetime
* Contractor (with country)

In the below code chunk, I load the data into R and do some preliminary data exploration to understand what data is contained in the dataset. 

```{r loading_data}
satellite_info <- read_excel("UCS_Satellite_Database_4-1-2019.xlsx") %>% clean_names()

satellite_info <- satellite_info %>% select(name_of_satellite_alternate_names:comments)
names(satellite_info)
dim(satellite_info)
#str(satellite_info)
```

In the above code chunk, I read in and edit the dataset to convert it into a more usable format. I replaced the spaces in the column names with underscores ("_") using clean_names() and selected only the columns with information in them, deleting the empty columns in the dataset. The dataset has dimensions of 2062X27, ie, it has 2062 observations over 27 variables. Most of the information is in character format, while the technical information is either numeric or doubles. 

Now, we can write assert functions to check the dataset and clean it.

```{r assert/verify}
is.date <- function(x) {
  !all(is.na(as.Date(as.character(x),format="%y/%m/%d")))
}

satellite_info %>% assert(is.date(satellite_info$date_of_launch)) #check if the values are in the correct date format

satellite_info %>% verify(perigee_km > 0) #perigee can have values only greater than 0km
satellite_info %>% verify(apogee_km > 0) #apogee can have values only greater than 0km

# Eccentricity is a feature that always has values greater than 0. This dataset contains 1 error. That observation is being filtered out to have a correct dataset.
satellite_info <-  satellite_info %>% filter(eccentricity >= 0)
satellite_info %>% verify(eccentricity>=0)

satellite_info %>% verify(period_minutes>=0) #Period of a satellite can have values only greater than 0 mins.
```

# Defining the problem

Some interesting things that I noticed while exploring the data was the breakup of satellites by country, and purpose. Each satellite has numerous associated variables related to its own features or that of its orbit. In this project, I will try and determine the variables controlling the purpose that the satellite is being used for. 

Motivating question(s): 1) Predict the purpose of a satellite based on other information provided regarding Orbital information and other associated information. 

